Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-21 latex/comp_or.tex
Comp OR paper update

We converted {\it Shims} into a process-based parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it surpassed all {\it Shims} results.

@@

\begin{keyword}
Air Cargo \sep Air Palletization \sep Weight and Balance \sep Pickup and Delivery \sep Parallel computing \sep iRace
\end{keyword}

@@

In this work, we raise four hypotheses for improvements to the work of \cite{MesquitaSanches2023}:
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.
(4) A post-optimization procedure for 3D packing running in parallel mode would keep the run time adequate for operational use.

@@

@@

The final experiments are performed on a 64-bit, 16GiB, 3.6GHz, 8-core AMD® Fx-8320e processor, 2 threads per core, with {\it Linux Ubuntu 20} as the operational system and {\it Python 3.8.2} as the programming language.

A relevant problem with meta-heuristics is the parameter's adjustment to extract the best possible efficiency in the optimization. The bulk of the tools to fine-tune these parameters utilize a statistical backdrop that enables them to make accurate predictions regarding the differences in candidate configurations' performance. Inadequacies in the design of the statistical experiment may therefore lead to erroneous results from the statistical tests and, subsequently, cause the approach to produce inaccurate comparisons of candidate configurations. That is why all parameters were set using the $iRace$ package \citep{LopezIbanezManuel2016}. Supplying $iRace$ with a range for $volThreshold$ as [0.80 to 0.99], {\it iRace} yielded 0.92, by training on the uneven instances numbers. The values tested for 20\%, 50\%, and 100\% volume surpluses were very close, considering the confidence level offered by {\it iRace}.

@@

According to \cite[p.271]{Breshears2009}, a {\it Process} is the operating system’s spawned and controlled entity that encapsulates an executing application. A process has two main jobs: the first is to hold the application's resources, and the second is to carry out the application's instructions.

It is known that working concurrently opens up synchronization issues. But the {\it Multi-processing} package (mp) offers both local and remote concurrency, effectively side-stepping the global interpreter lock by using sub-processes instead of threads. Because of this, the {\it Multi-processing} module lets the programmer take full advantage of the fact that a machine has more than one processor, normally capable of 2 threads each.

By Amdahl's law, there is an optimal number of parallel executions for each problem in each environment. While working at IBM in 1967, Gene Amdahl developed the foundation for what became known as Amdahl's Law or Amdahl's Argument. Essentially, the law states that while a process can be decomposed into steps that may then be run in parallel, the time taken for the whole process will be significantly limited by the steps that remain serialized.

@@

We confirmed the hypothesis raised in line \ref{mpShims:minCGdev} of Algorithm \ref{alg:mpShims} that, in sequential mode, where one pallet is built at a time, torque constraints could be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. This integer programming procedure inclusion really improved all {\it Shims} results.

@@

\subsection{Another possible improvement}
\label{improvement}

@@

In this work, we raised four hypotheses for improvements to the work of \cite{MesquitaSanches2023}:

>>>>

We converted {\it Shims} into a process-based parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it surpassed all {\it Shims} results. We also solved a three-dimensional packing problem in the item-pallet allocations yielded by {\it Shims}.

@@

\begin{keyword}
Air Cargo \sep Air Palletization \sep Weight and Balance \sep Pickup and Delivery \sep Parallel computing \sep 3D packing
\end{keyword}

@@

In this work, we raise four hypotheses for improvements to the work of \cite{MesquitaSanches2023}: \label{hypotheses}
(1) Computer parallelism could improve {\it Shims}'s performance.
(2) The {\it Shims}' results may have been inferior to that; it could be that a sequential approach to pallet building may lead to a premature stop due to the torque constraints.
(3) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.
(4) A post-optimization procedure for 3D packing running in parallel mode would keep the run time adequate for operational use.

@@

The final experiments are performed on a 64-bit, 16GiB, 3.4GHz, 8-core Intel® i7-3770 CPU, 2 threads per core, with {\it Linux Ubuntu 22.04 LTS} as the operational system and {\it Python 3.10.6} as the programming language.

@@

A relevant problem with meta-heuristics is the parameter's adjustment to extract the best possible efficiency in the optimization. The bulk of the tools to fine-tune these parameters utilize a statistical backdrop that enables them to make accurate predictions regarding the differences in candidate configurations' performance. Inadequacies in the design of the statistical experiment may therefore lead to erroneous results from the statistical tests and, subsequently, cause the approach to produce inaccurate comparisons of candidate configurations. That is why all parameters were set using the $iRace$ package \cite{LopezIbanezManuel2016}. Supplying $iRace$ with a range for $volThreshold$ as [0.80 to 0.99], {\it iRace} yielded 0.92, by training on the uneven instances numbers. The values tested for 20\%, 50\%, and 100\% volume surpluses were very close, considering the confidence level offered by {\it iRace}.

@@

According to \citet[p.271]{Breshears2009}, a {\it Process} is the operating system’s spawned and controlled entity that encapsulates an executing application. A process has two main jobs: the first is to hold the application's resources, and the second is to carry out the application's instructions.

It is known that working concurrently opens up synchronization issues. But the {\it Multi-processing} package ({\it mp}) offers both local and remote concurrency, effectively side-stepping the global interpreter lock by using sub-processes instead of threads. Because of this, the {\it Multi-processing} module lets the programmer take full advantage of the fact that a machine has more than one processor, normally capable of 2 threads each.

By Amdahl's law, there is an optimal number of parallel executions for each problem in each environment. While working at IBM in 1967, Gene Amdahl developed the foundation for what became known as Amdahl's Law or Amdahl's Argument. Essentially, the law states that while a process can be decomposed into steps that may then be run in parallel, the time taken for the whole process will be significantly limited by the steps that remain serialized. In our case, the reading and writing process on the shared torque variable and the list of items to be embarked.

@@

We confirmed the hypothesis raised in \ref{hypotheses} and in line \ref{mpShims:minCGdev} of Algorithm \ref{alg:mpShims} that, in sequential mode, where one pallet is built at a time, torque constraints could be more restrictive than volume or weight constraints, which could stop the palletization process earlier, yielding a solution that may be not as good as it could be. This integer programming procedure inclusion really improved all {\it Shims} results.

@@

\subsection{An attempt to minimize ground handling time}
\label{improvement}

@@

In this work, we raised four hypotheses for improvements to the work of \cite{MesquitaSanches2023}: \label{hypotheses}
